A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotide distribution

### 2013-04-11 ISMB/Camera/Waldispuhl.337.tex
typos corrected
fix fig links
typo title

\title{A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotides distribution}
\author{Vladimir Reinharz$^1$, Yann Ponty$^{2,*}$, J\'er\^{o}me Waldisp\"{u}hl$^{1}$\footnote{to whom correspondence should be addressed}}
\address{$^1$ School of Computer Science, McGill University, Montreal, Canada\\ $^2$ Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.}

@@

\begin{figure}[ht!]
	\centering
 	\includegraphics[width=0.5\textwidth]{Waldispuhl.337.fig.3.pdf}
	\caption{
  Average time in seconds to generate one sequence for \ourprog and \RNAinverse.}
	\label{fig:time}	
\end{figure}

@@

 \begin{figure*}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{Waldispuhl.337.fig.4.pdf}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure*}

@@

\begin{figure}[ht!]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{Waldispuhl.337.fig.5.pdf}
  \end{center}
  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse, \INFORNA, \NUPACK and \frankenstein folding in the desired structure.}
  \label{fig:gcdist}
\end{figure}

@@

\begin{figure*}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{Waldispuhl.337.fig.6.pdf}
	\caption{Success rate \ourprog before and after \RNAinverse post-processing. The first row shows the percentage of sampled sequences folding into the target when using only \ourprog. The second shows after processing previous results with \RNAinverse.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure*}

@@

\begin{figure*}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{Waldispuhl.337.fig.7.pdf}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure*}

@@

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Waldispuhl.337.fig.8.pdf}
	\caption{Number of solutions generated with \ourprog+\RNAinverse on the first row and their average sequence identity on the second.} 
	\label{fig:nb_sols_entropy}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Waldispuhl.337.fig.9.pdf}
	\caption{Thermodynamical stability of the target structure. The curves report the average Boltzmann probability of the target structure (which is also the MFE structure) at various {\GCContent}s w.r.t. the length of the target (left), density of stacked base pairs (centre) and number of unpaired nucleotides  in loops (right).}
	\label{fig:freq}
\end{figure*}

@@

To conclude this study, we estimate the impact of the design methodology on the performances. More precisely, we aim to determine the merits of a global sampling approach (\ourprog), compared to a glocal procedure (\ourprog + \RNAinverse) and a local search methodology (\RNASSD). To our knowledge, \RNASSD, beside \ourprog, is the only software that implements an explicit control of the \GCContent.

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{Waldispuhl.337.fig.10.pdf}
  \caption{Sequence identity of \ourprog and \RNAinverse for $10$ and $30\%$ of \GC.}
  \label{fig:benchmark_RNASSD}
\end{figure*}

>>>>

\title{A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotide distribution}
\author{Vladimir Reinharz$^1$, Yann Ponty$^{2,*}$, J\'er\^{o}me Waldisp\"{u}hl$^{1}$\footnote{to whom correspondence should be addressed}}
\address{$^1$ School of Computer Science, McGill University, Montreal, Canada\\ $^2$ Laboratoire d'informatique, \'Ecole Polytechnique, Palaiseau, France.}

@@

\begin{figure}[ht!]
	\centering
 	\includegraphics[width=0.5\textwidth]{{Waldispuhl.337.fig.3}.pdf}
	\caption{
  Average time in seconds to generate one sequence for \ourprog and \RNAinverse.}
	\label{fig:time}	
\end{figure}

@@

 \begin{figure*}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.4}.pdf}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure*}

@@

\begin{figure}[ht!]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{{Waldispuhl.337.fig.5}.pdf}
  \end{center}
  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse, \INFORNA, \NUPACK and \frankenstein folding in the desired structure.}
  \label{fig:gcdist}
\end{figure}

@@

\begin{figure*}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.6}.pdf}
	\caption{Success rate \ourprog before and after \RNAinverse post-processing. The first row shows the percentage of sampled sequences folding into the target when using only \ourprog. The second shows after processing previous results with \RNAinverse.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure*}

@@

\begin{figure*}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.7}.pdf}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure*}

@@

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.8}.pdf}
	\caption{Number of solutions generated with \ourprog+\RNAinverse on the first row and their average sequence identity on the second.} 
	\label{fig:nb_sols_entropy}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.9}.pdf}
	\caption{Thermodynamical stability of the target structure. The curves report the average Boltzmann probability of the target structure (which is also the MFE structure) at various {\GCContent}s w.r.t. the length of the target (left), density of stacked base pairs (centre) and number of unpaired nucleotides  in loops (right).}
	\label{fig:freq}
\end{figure*}

@@

To conclude this study, we estimate the impact of the design methodology on the performances. More precisely, we aim to determine the merits of a global sampling approach (\ourprog), compared to a glocal procedure (\ourprog + \RNAinverse) and a local search methodology (\RNASSD). To the best of our knowledge, \RNASSD, beside \ourprog, is the only software that implements an explicit control of the \GCContent.

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\textwidth]{{Waldispuhl.337.fig.10}.pdf}
  \caption{Sequence identity of \ourprog and \RNAinverse for $10$ and $30\%$ of \GC.}
  \label{fig:benchmark_RNASSD}
\end{figure*}
